\myTitle

### 2024-07-11 cover-letter/gscramble-cover-letter.tex
Update gscramble-cover-letter.tex
typo

The approach we have developed is implemented in the R package `gscramble' which
is currently available for download from the Comprehensive R Archive
Network (CRAN), and includes full documenation and vignettes.
Members of our team have used `gscramble' already in one published project and
the package is currently in use in several more.   We predict that the package will be
widely used in the future, and as a consequence, the paper will be highly cited.

>>>>

The approach we have developed is implemented in the R package `gscramble' which
is currently available for download from the Comprehensive R Archive
Network (CRAN), and includes full documentation and vignettes.
Members of our team have used `gscramble' already in one published project and
the package is currently in use in several more.   We predict that the package will be
widely used in the future, and as a consequence, the paper will be highly cited.
